Project

### 2022-04-01 Project/DraftR.Rmd
Update DraftR.Rmd

# Climate Effect Analysis
## Data Check and Modification
```{r}
sapply(clim, class)
```
```{r}
#variable explanation:
  #d.snowpack.10.11 = days with snowpack winter 2010-2011
  #wTmin.10.11 = minimum temperature winter (C) at plant height 2010-2011
  #Dec.FebTav.10.11 = mean temperature at plant height from Dec1st 2010 - Feb 28th 2011
  #d.grows.11 = # days in growing season 2011 (start / end of gorwing season determined by sustained snow or frost)
  #GDD.grows.11 = # growing degree days (Tbase=10C, Tmax capped at 30C) in growing season of 2011
  #GDD.yr.11 = # growing degree days in 2011 (ie not truncated to estimated growing season)
  #avmaxminTJuly.11 = mean July 2011 temperature (C) calculated from daily min and max T: 
      ##mean(July1stmin + July1stmax + July2ndmin + July2ndmax + ... July31stmi + July31stmax)
  #avTJuly.11 = mean July 2011 temperature (C) calculated from raw data (ie >2 measurements per day)

@@

head(clim.me)
```
```{r}
#use 'dcast' to cast the molten data.frame into a data frame
clim.ca <- dcast(clim.me, ID + year ~ variable)
head(clim.ca)
```
# Phenology Analysis
## Combine Datasets and Subset 
```{r}

>>>>

# Climate Effect Analysis
## Data Check and Modification
```{r}
sapply(clim, class)
```
```{r}
#variable explanation:
##winter limited:
  #d.snowpack.10.11 = days with snowpack winter 2010-2011
  #wTmin.10.11 = minimum temperature winter (C) at plant height 2010-2011
  #Dec.FebTav.10.11 = mean temperature at plant height from Dec1st 2010 - Feb 28th 2011
##
  #d.grows.11 = # days in growing season 2011 (start / end of gorwing season determined by sustained snow or frost)
  #GDD.grows.11 = # growing degree days (Tbase=10C, Tmax capped at 30C) in growing season of 2011
  #GDD.yr.11 = # growing degree days in 2011 (ie not truncated to estimated growing season)
  #avmaxminTJuly.11 = mean July 2011 temperature (C) calculated from daily min and max T: 
      ##mean(July1stmin + July1stmax + July2ndmin + July2ndmax + ... July31stmi + July31stmax)
  #avTJuly.11 = mean July 2011 temperature (C) calculated from raw data (ie >2 measurements per day)

@@

head(clim.me)
```
```{r}
#use 'dcast' to cast the molten data.frame into a data frame
clim.ca <- dcast(clim.me, ID + year ~ variable)
clim.ca$year <- as.factor(clim.ca$year)
head(clim.ca)
```
```{r}
#select all rows that contains winter season info and columns related to winter
clim.win <- subset(clim.ca, subset = year %in% c("winter 10-11", "winter 11-12", "winter 12-13", "winter 13-14"),
                   select=c(ID, year, d.snowpack, Dec.FebTav, wTmin))
head(clim.win)
```

```{r}
#select all rows that contains season info except for winter and columns related
clim.not.win <- subset(clim.ca, subset = year %in% c("year 2011", "year 2012", "year 2013"),
                   select=-c(d.snowpack, Dec.FebTav, wTmin))
head(clim.not.win)
```

```{r}
climDist <- dist(clim.ca, method = 'euclidean')
climDistMat <- as.matrix(climDist)
# rearrange the data from an n×n matrix to a n2×3 matrix
climPDat <- melt(climDistMat)
climPDat
# plot the matrix
ggplot(data = climPDat, aes(x = Var1, y = Var2, fill = value)) +
  geom_tile() +
  scale_fill_gradientn(colours = c("white","blue","green","red")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))
```

# Phenology Analysis
## Combine Datasets and Subset 
```{r}
